### 2015-01-14 etc/abstract.tex
update abstract

% 1.Statetheproblem
Mutation analysis is a well-known method for measuring the quality of
test suites. However, it is computationally intensive compared to
other measures, which makes it hard to use in practice. Choosing a
smaller subset of mutations to run is a simple approach that can
alleviate this problem.  Mutation operator selection has been heavily
researched. Recently, researchers have found that sampling mutants can
achieve accuracy and mutant reduction similar to operator selection.
Newer research has also indicated that program element based sampling
may be better than pure random sampling or traditional operator selection.

%
%2.Saywhyit’saninterestingproblem
However, the empirical support for these conclusions has been limited,
due to the small number of subject programs investigated. The best sampling
technique is also an open problem. Further, current research has focused
on evaluating mutation analysis techniques over adequate test suites. However,
real world test suites are often far from test adequacy, and it is not clear
if the results carry over to non-adequate test suites.
%3.Saywhatyoursolutionachieves

We propose that a better mutation selection criteria should generate a larger
number of defective behaviors than a worse mutation selection criteria, which
we judge using the number of non-redundant tests able to kill the sampled
mutants.

We evaluate the performance of various selection criteria on 250 opensource
projects from github, which shows that the popular operator selection and
element based sampling are not much better than random selection, and often
performs worse than random selection. This suggests a need for further research
on better methods of operator selection and sampling.

>>>>

% 1.Statetheproblem
Mutation analysis is a well-known method for measuring the quality of
test suites. However, it is computationally intensive compared to
other measures, which makes it hard to use in practice. Multiple
strategies has been proposed to reduce the number of mutants produced,
and hence reduce the computational requirements.

%
%2.Saywhyit’saninterestingproblem
However, current research on mutation reduction is beset with several
problems. There is inconclusive evidence supporting many of the suggested
reduction strategies due to the limited number and size of of subject
programs investigated. The lack of a comprehensive study comparing
at-least the major approaches is another problem. Finally the traditional
evaluation criteria for mutation reduction approaches relies on
mutation-adequate test suites which rarely occur in real world. There is
little evidence that the strategies that perform well using the traditional
evaluation crtiera leads to better mutation selection for non-adequate
tests in the real world.

%3.Saywhatyoursolutionachieves

We extend the traditional reduction crtieria so that it is usable with
non-mutation adequate test suites, and link it to the actual use of
mutation analysis during development -- to produce tests that check for
as many different bugs as possible.

We evaluate the performance of various selection criteria on 312 opensource
projects from github, which shows that the popular reduction strategies:
operator selection, operator based sampling, and element based sampling
are hardly better than random selection, and often performs worse.
This suggests a need for further research on better methods of mutation
reduction strategies.
